Conformance Checking Using Embeddings and it's Applicability in the Internet of Things

### 2021-12-19 paper.tex
Discovery plot

\subsection{Discovery Experiment}

The purpose of the last experiment was the comparison of the three proposed techniques to establish conformance checking algorithms.
The results of this experiment can be found in \cite{PBWe20} Table 5.
\todo{Include their data? Manually as table or maybe as plot. If so what kind plot would you suggest}
The results from the discovery experiment seem to suggest that all three methods are able to capture a notion of conformance.
Especially when the model is of high quality both the proposed and validation conformance checking techniques often agree on a perfect score.
However, it should be noted that there are quite a few instances where all three proposed methods assign perfect fitness or precision despite the others producing imperfect scores.
This is worrying since one of the most basic requirements for a good conformance checking technique is not assigning perfect scores to models that are able to replay fewer or more traces than in the log.
It is unclear whether that is due to the unoptimized nature of the methods, it could be the case that the methods are not sensitive enough, which could be fixed by varying the parameters, or due to the limited size of the model logs, which were limited to 1000 traces, which puts an upper limit on the amount of behavior that the embeddings are able to observe.

>>>>

\subsection{Discovery Experiment}
\begin{figure}
	\centering
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\textwidth]{figures/fitness}
		\caption{Fitness}
		\label{fig:fitness}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\textwidth]{figures/precision}
		\caption{Precision}
		\label{fig:precision}
	\end{subfigure}
\caption{Fitness and Precision for different tree, discovery technique pairings for the three proposed techniques as well as the two verification techniques. 
	Note that values are shown for WMD,ICT and \emph{trace2vec} are mirrored along x, since they are not proper metrics and larger values means worse fitness/precision. 
	This way all results move in the same direction for better/worse values.
Raw data can be found in \cite{PBWe20} Table 5.}
\label{fig:discovery}
\end{figure}

The purpose of the last experiment was the comparison of the three proposed techniques to establish conformance checking algorithms.
The results of this experiment can be found in \cref{fig:discovery}.
The results from the discovery experiment seem to suggest that all three methods are able to capture a notion of conformance.
Especially when the model is of high quality both the proposed and validation conformance checking techniques often agree on a perfect score.
However, it should be noted that there are quite a few instances where all three proposed methods assign perfect fitness or precision despite the others producing imperfect scores.
This is worrying since one of the most basic requirements for a good conformance checking technique is not assigning perfect scores to models that are able to replay fewer or more traces than in the log.
It is unclear whether that is due to the unoptimized nature of the methods, it could be the case that the methods are not sensitive enough, which could be fixed by varying the parameters, or due to the limited size of the model logs, which were limited to 1000 traces, which puts an upper limit on the amount of behavior that the embeddings are able to observe.
